Title

### 2023-11-17 Response to Reviewers.tex

\section*{Reviewers' General Comments}

\textbf{Reviewer 1:} \\

\textbf{
The paper presents two results: 1. A way to simulate
parametric Pauli Channels using a gate-based formalism, useful for
quantum computation, and 2. An investigation on the class of
parametric Pauli Channels that can be parametrised by acting only on
one qubit via one parameter.
The full detailed comments on the paper are attached in the pdf file.
My general comments are the following:
\begin{itemize}
\item[1.]The two aforementioned results are disjointed and completely
lacking in motivation. The entire logic of the paper is obscure, and
seemingly lacks any ground for the results to be useful in any way.
\item[2.] The simulation on the IBM quantum computer is irrelevant, and does
not prove neither the validity of the decomposition (as it fails for
most of the range of operations) nor it is quantifiying any relevant
parameter (noise for example). Data from those experimental runs and
complete methodology for calculating the diamond norm is also missing.
\item[3.] The claims are vague, and the mathematical formalism is vague, with
strong abuse of notation and non-strict definitions and theorems.
There are also many spelling mistakes and refuses, even in the
formulas.
\item[4.] The analysis on the 1-parametrisation is lacking a discussion on
what happens at higher than 2 dimensions.
\end{itemize}
For the aformenetioned reasons, I cannot reccomend this paper for
publication. I suggest the following three course of actions:
\begin{itemize}
\item[1.] Separate the two main results.
\item[2.]Improve the tightness of the mathematical formalism.
\item[3.]  Find an application of the generalised Pauli Channels that can be
effectively simulated with the methodology.
\end{itemize}
}

We thank the first reviewer for the time spent carefully 
assessing the manuscript, and the opinions given.
We have made major changes in the manuscript following your comments and recommendations. 
Some of the general changes we made are explained in the following list
and then we respond to more specific comments
throughout the text.
\begin{itemize}
\item We rewrote big parts of the introduction to make clearer the logic and motivation of the paper. 
We begin the paper by presenting the theory of Pauli channels, 
and then show the first result, which is the algorithm for simulating them on a quantum computer,
which we try out for systems of one and two qubits.
With that algorithm in mind, we seek to generalize it to Pauli dynamical maps, 
so as to include continuous transformations of the 
N-qubit system. This goal leads us to
focus on parametrized quantum circuits and then to consider
what can be done with only moving one parameter.
\item We added the data and code from the IBM quantum computer simulations
to a Github repository: \href{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}
\item We improved the tightness of the mathematical formulation by adding
a more mathematical definition of 1PR circuits and
rephrasing the proof of theorem 2 to make it clearer. 
The specific changes are discussed below as responses to the comments made by the reviewer throughout the text.
\item In section 5 of the paper we expanded the explanations on the examples for Pauli dynamical maps
that can be implemented with a 1PR circuit.
These Pauli dynamical maps are well-known and we prove here
that they can be done with only moving one parameter in the circuit. We also added explicitly the matrices $A$ and $B$ that can
be used to simulate them with a 1PR circuit.
Furthermore, we included Fig. 8, where
we show the results of implementing these dynamical circuits on IBM's computer using a 1PR circuit.

@@

\textbf{While the implementations appear to be mathematically sound, there
appears to be a lack of comparisons between the actual channel
implemented and the target channel. There is only one Fig. 3 that
shows the diamond fidelities for homogenously-chosen single-qubit
unparametrized Pauli target channels within the tetrahedron region.
This is a nice plot that reveals the realistic errors coming from the
IBM quantum cloud, namely that the single-qubit Pauli channels
corresponding to the central part, which I presume are the
depolarizing channels, have the highest diamond fidelity.}

\textbf{
Besides this plot, the authors however did not show the performance of
their algorithms for larger number of qubits, and there are no
performance plots for dynamical Pauli-channel implementations. For a
further evaluation as to whether the algorithms are scientifically
practical, at least a plot on two-qubit Pauli channels and one on
two-qubit dynamical Pauli channels. My take is that because the
unitary operators A and B are too sophisticated for hardware
implementations, since they are even more complicated than single
controlled unitary operators, the fidelity could be very strongly
peaked around the zero of the pseudo Bloch-vector space for multiqubit
systems. If the overall system is too large even for simulating
two-qubit channels (due to the ancillas), then classical numerical
simulations are sufficient.}

\textbf{
In any case, after supplying the performance plots, I believe that the
algorithms and performance plots shall supply a fair presentation on
the scientific soundness of this work.} \\$\;$\\

We thank the second reviewer for the detailed analysis
of our manuscript and the comments made. 
Following the recommendations, we 
added section 3.3 in which we simulate a two qubit Pauli dynamical map 
and in Fig. 4 show that the fidelities are still reasonably high.

Regarding the 1PR circuits, we added explicitly the matrices $A$ and $B$
to the examples of dynamical maps and
simulated them on IBM's quantum computer
using the dynamical Pauli channel implementation.
For each of these simulations, we used the proposed 1PR circuit and plotted  in Fig. 8 the fidelities for
different channels along the dynamical map.

Finally, we included a paragraph in the conclusion discussing what happens on higher dimensions and arguing that paradigmatic
channels such as the two qubit dephasing channel of section 3.3 will still have a 
1PR circuit implementation.

@@

\begin{enumerate}
\item \textbf{I fail to see the point here, the logic of the paper is: 
1. ``open quantum systems can be modeled through a class of channels representing he various types of decoherence.'' 2. ``Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.''
3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them.}

\textbf{What I am missing is what do we learn by doing it which cant be learned by actually performing the Pauli channel onto a quantum system? For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial. Why would I need to decompose (not even effectively for any channel) the pauli channels to match a gate based description? Which class of problems can we simulate that cannot be simulated otherwise? Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)}

\textbf{Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective. }\\

We rewrote parts of the introduction to make the objective of the manuscript clearer. 
First of all, one of the principal objectives of quantum computers nowadays
is to use them for simulation of quantum processes,
and out of all quantum processes, decoherence is one of the most important and prevalent.
That is why we chose to simulate Pauli channels, which are one of the
simplest descriptions of decoherence. 
Important characteristics about the algorithm proposed for Pauli channels
are its simplicity and generality.
We chose to represent the channel using a gate-based formalism because
of it being one of the most common and general ways of
representing quantum algorithms.

Furthermore, the simplicity and generality of the circuit proposed allows us to
naturally generalize it to Pauli dynamical maps by just
adding movable parameters to the circuit.
Finally, we show the general result of what parametrized quantum operations can be done 
moving only one parameter, which experimentally could translate
to having to adapt only one setting of an experiment
to simulate the quantum operation.

@@

We added a few lines at the beginning of section 3 defining the concept of quantum circuit.
We  mention that quantum circuits are a representation of computation on quantum systems, which applies a unitary operator $U$.

\item  \textbf{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.}\\

The algorithm works to some extent for all Pauli channels, and how well
it does or does not work is quantified by the fidelity.
Indeed, the result we got is that it works much better for channels that are depolarizing
and less well as we get closer to unitary channels.

\item \textbf{Why?}\\
We rephrased the sentence to make the point clearer
and explained that as a consequence of the circuit being usable in general for any Pauli channel,
it implements unitary channels in a very roundabout way.

@@

\item \textbf{But this is a severe disadvantage, that begs the question: what is the advantage?} \\

The advantages are that it is a straightforward, concrete and general way
of simulating Pauli channels.
Being general gives the possibility to later use it for Pauli dynamical maps by only needing to vary the parameters
and not the design of the circuit itself.

@@

\item \textbf{This definition is vague - given the vagueness of the term "quantum circuit".
 Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit. } \\

We added a sentence explaining that to make it more concrete.

\item \textbf{Normal}\\

They are only orthogonal, since their individual norms are not equal to $1$. 
After restructuring the proof of theorem 2, this is now clearer.

@@

\item \textbf{Again, this is not a conclusion from theorem 1. This is literally Definition 1. Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N. Then the matrix representation of the operators is a $2^n\times 2^n$ matrix which is applied to the state j. The explanation in words in not sufficient.} \\

We rephrased the first paragraph of the proof to make it easier to see when we use the result of theorem 1. 
Basically, we first use definition 1 to say that the circuit has the form $ARB$,
and then the result of theorem $1$
to conclude that $R$ is in particular a $\sigma_3$ rotation
of angle $2s$ applied to the last qubit.\\

@@

\item \textbf{True only if the initial j states are normalised, but they were undefined.}\\

We added the definition of $|j\rangle$  at the end of the theorem statement.\\

\item \textbf{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?}\\

We changed the phrasing to make it clearer that $A$ and $B$ 
are restricted to act in a particular way on the last 3 and first qubit respectively.
Besides from that, the remaining parts of the operators $A$ and $B$ can be chosen arbitrarily, 
with the only restriction that the resulting matrices are unitary. \\

@@

\item  \textbf{Please, at least give an example of this semiarbitrary construction of A and B.}\\

We added examples of these matrices for the particular dynamical maps shown in section 5. \\

@@

 \item  \textbf{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit. I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so.. what is the applicability of the theorem for higher dimensions?} \\

We added a paragraph in the conclusion talking about that.
There we argue that for bigger systems, the space of dynamical maps
that can be implemented with a 1PR circuit
is a smaller part of the whole space of dynamical maps.
However, some of the most paradigmatic maps will still be implementable this way.

\item \textbf{Imprecise} \\

We have rephrased parts of the conclusion to make it clearer.

### 2023-11-17 main.tex
Cambios-carta

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts towards the
simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
and specifically for quantum channels~\cite{Xin,Wei,Zanetti}, 
which can be used to study and model decoherence.
Such quantum algorithms can be represented using what is known as a quantum
circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.

>>>>

Since their inception, quantum computers were proposed as powerful tools for
the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
practical~\cite{breuer2007theory} interest, there has been efforts towards the
simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
and specifically for quantum channels~\cite{He-Lu,Xin,Wei,Zanetti}, 
which can be used to study and model decoherence.
Such quantum algorithms can be represented using what is known as a quantum
circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.
